---
title: "Female Pulse Rates"
format: html
editor: source
execute:
  echo: false
  warning: false
  message: false
---

## Question
What is the difference in pulse rate between two randomly selected female students in this class?

```{r}
library(tidyverse)
library(primer.data)
library(rstanarm)
```

```{r}
# nhanes
```
```{r}
x = nhanes |>
  filter(gender == "Female") |>
  select(pulse) |>
  drop_na()
```
```{r}
x |>
  ggplot(aes(x = pulse)) +
  geom_histogram(aes(y=after_stat(count/sum(count))), binwidth = 1) +
  scale_y_continuous(labels = scales::percent_format())
```
```{r}
fit_obj = stan_glm(data = x,
                   formula = pulse ~ 1,
                   family = gaussian,
                   refresh = 0,
                   seed = 9)
# fit_obj
```
```{r}
newobs = tibble(.rows = 2)

pp = posterior_predict(fit_obj,
                       newdata = newobs) |>
  as_tibble() |>
  mutate(diff = abs(`2`-`1`))
# pp
```
```{r}
pp |>
  ggplot(aes(x = diff)) +
  geom_histogram(aes(y = after_stat(count/sum(count))), bins = 100) +
  theme_classic() +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(title = "Posterior for the difference between two randomly selected female students",
       x = "Difference in Pulse (bpm)",
       y = "Probability")
```


## Wisdom

### predictive or causal
predictive

### units
individual females

### outcome
difference of two randomly selected pulses

### covariates

### Preceptor Table
All the female pulses in this class

### validity
inconsistent medical equipment
training of people calculating the pulse
walking around/sitting down


### Population Table
rows: students
column: pulse


## Justice

### representitiveness
age of females could be different
The data focuses more on minority groups

### stability
people will get more nervous as the world might end

### unconfoundedness
not a causal problem

## Courage

## Wisdom

